Local Type Inference for Polarised System F with Existentials

### 2023-10-12 oopsla24/tex/01-introduction.tex
some narrative for the intro

ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

>>>>

% How we should frame this:

\begin{itemize}
\item There has been very little work on type inference for existentials. 
\item The state of the art in languages like Ocaml and Haskell is the
  Odersky-L\"{a}ufer algorithm, which makes existentials a
  second-class construct tied to datatypes.
\item More recently, there's the existential crisis paper, which
  showed how to extend ML-style inference with some support for
  existentials. However, it is (a) predicative-only, (b) restricted
  for $\forall\exists$ types, and (c) does not have a declarative
  specification. (In fact, the authors comment on the need for such.)
\item In this paper, we lift all of these restrictions. We give a
  local type inference algorithm which supports first-class
  existentials, for impredicative types, with no restrictions on
  nested quantifers, and we have declarative specification we prove
  our algorithm sound and complete with respect to.
\item Developing the algorithm required us to break some of the
  fundamental invariants of HM-style typin, and as a result, our
  algorithm needs to mix unification and anti-unification, and works
  over a call-by-push-value metalanguage to control how quantifiers
  are instantiated and things like function arities.
\item Unfortunately, local type inference does not infer types anywhere
  nearly as comprehensively as full Damas-Milner type inference. We
  do guarantee that all type applications (for $\forall$-elimination) 
  and all packs (for $\exists$-introdution) are inferred, but functions
  and some let-bindings still need annotations on their arguments.
\item The original local type inference paper combined local type inference
  with bidirectional typechecking to minimize the number of needed
  annotations, but we show how existential types complicate the integration
  of bidirectionality with local type inference, and we explore the design space
  to show how the same scheme could be applied to work with different
  type systems. 
\end{itemize}

\nk{We need to explain what local type inference is, and how it is and isn't
  related to bidirectional typechecking.}
